fl0w - a development environment for the\\ KIPR Wallaby

### 2017-04-01 paper.tex
Fixed references leaking onto 5th page

\subsubsection{Protocol}
behem0th\cite{behem0th:Christoph Heiss} is independent from underg0und and defines its own network protocol. It is completely text-based, uses UTF-8\cite{UTF-8:F. Yergeau} for character encoding and JSON\cite{JSON:T. Bray Ed.} as format encoding. behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'. Each request is a JSON-formatted string and separated by a newline.

@@

\subsubsection{Discovery process}
Upon launch disc0very\cite{disc0very:Christoph Heiss} listens for advertisements from an already running fl0w\cite{fl0w:Philip Trauner} server. If an advertisement is received the client-mode is engaged and a connection to the server is established. If no advertisement has been received after 2s server-mode is engaged. Server-mode can be disabled for clients that do not have the capability to become a server, for example edit0r\cite{edit0r:Philip Trauner}).

@@

\bibitem{fl0w:Philip Trauner}
Philip Trauner, Christoph Heiss, Sebastian Schaffler, \emph{fl0w}, \url{https://github.com/robot0nfire/fl0w},\\ source code,
accessed February 9th 2017

\bibitem{Harrogate:KIPR}
KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate},\\ source code,
accessed February 9th 2017

@@

\bibitem{Wallaby Controller:KIPR}
KIPR, \emph{Wallaby Controller},  \url{http://botballstore.org/product/wallaby-controller}, \\ store page, accessed February 9th 2017

@@

\bibitem{ECMAScript:Ecma}
Ecma International, \emph{ECMAScript}, \url{https://www.ecma-international.org/ecma-262/7.0/index.html},\\ language specification,
accessed February 12th 2017

@@

\bibitem{UTF-8:F. Yergeau}
F. Yergeau, \emph{UTF-8}, \url{https://tools.ietf.org/html/rfc3629},\\ request for comment,
accessed March 22nd 2017

@@

\bibitem{edit0r:Philip Trauner}
Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w},\\ source code, accessed February 9th 2017

\bibitem{disc0very:Christoph Heiss}
Christoph Heiss, \emph{disc0very}, \url{https://github.com/robot0nfire/fl0w/blob/master/Shared/Disc0very.py},\\ source code, accessed March 30th 2017

>>>>

\subsubsection{Protocol}
behem0th\cite{behem0th:Christoph Heiss} is independent from underg0und and defines its own network protocol. It is completely text-based, uses UTF-8 for character encoding and JSON\cite{JSON:T. Bray Ed.} as format encoding. behem0th is designed around 'requests' $($see Figure ~\ref{fig:behem0th_request}$)$ and 'routes'. Each request is a JSON-formatted string and separated by a newline.

@@

\subsubsection{Discovery process}
Upon launch disc0very\cite{disc0very:Christoph Heiss} listens for advertisements from an already running fl0w\cite{fl0w:Philip Trauner} server. If an advertisement is received the client-mode is engaged and a connection to the server is established. If no advertisement has been received after 2s server-mode is engaged.

@@

\bibitem{fl0w:Philip Trauner}
Philip Trauner, Christoph Heiss, Sebastian Schaffler, \emph{fl0w}, \url{https://github.com/robot0nfire/fl0w}, source code,
accessed February 9th 2017

\bibitem{Harrogate:KIPR}
KIPR, \emph{Harrogate}, \url{https://github.com/kipr/harrogate}, \\ source code,
accessed February 9th 2017

@@

\bibitem{Wallaby Controller:KIPR}
KIPR, \emph{Wallaby Controller},\\  \url{http://botballstore.org/product/wallaby-controller}, store page, accessed February 9th 2017

@@

\bibitem{ECMAScript:Ecma}
Ecma International, \emph{ECMAScript}, \\\url{https://www.ecma-international.org/ecma-262/7.0/index.html}, language specification, accessed February 12th 2017

@@

@@

\bibitem{edit0r:Philip Trauner}
Philip Trauner, \emph{edit0r}, \url{https://github.com/robot0nfire/fl0w/tree/master/Sublime/fl0w}, source code, accessed February 9th 2017

\bibitem{disc0very:Christoph Heiss}
Christoph Heiss, \emph{disc0very}, \url{https://github.com/robot0nfire/fl0w/blob/master/Shared/Disc0very.py}, source code, accessed March 30th 2017
